Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-09-26 paper/main.tex
update main
update main.tex

\settopmatter{printacmref=false, printccs=true, printfolios=true}
\input{macros}

\title{\textbf{Notes of DP - Bayesian Inference}\\}
% \author{Jiawen \textsc{Liu}}
\date{\vspace{-10ex}}

\begin{document}
\maketitle

\section{Bayesian Inference Based on Dirichlet-Bernoulli Distribution}
\label{sec_bayesInfer}
In the Bayesian inference, first there is a prior distribution $\pi(\xis)$ to present our belief about parameter $\xis$. Then, we get some observed data $x$ sizing $n$, and produce a posterior distribution $Pr(\xis | x)$. The Bayesian inference is based on the Bayes' rule to calculate the posterior distribution:
\begin{equation*}
Pr(\xis | x) = \frac{Pr(x | \xis) \pi(\xis)}{Pr(x)}
\end{equation*}
It is denoted as $\bysinfer(x,\pi(\xis))$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, where $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$. $m$ is the order of the Dirichlet distribution.

We give a inference process based on a concrete example, where we throw an irregular $m$ sides dice. We want to infer the probability of getting each side $\xis$. We get a observed data set $\{s_{k_1}, s_{k_2}, \cdots, s_{k_n}\}$ by throwing the dice $n$ times, where $k_i \in \{1,2,\cdots, m\}$ denotes the side we get when we throw the dice the $i^{th}$ time. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the appearance time of the side $i$ in total.

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. The $m$ side dice change into a irregular coin with side $A$ and side $B$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.

@@

@@

\textbf{Detail proof:}
\begin{itemize}

	\item $\lambda < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		\end{equation*}
	\item $\lambda > 0$

@@

\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.

@@

\subsubsection{Accuracy Analysis wrt. prior distribution}
In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig. \ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{sensitivity}
\label{fig_sensitivity}
\caption{Hellinger distance study}
\end{figure}

@@

% \subsection{Experimental Evaluations on Accuracy}
% \label{subsec_experiment_accuracy}

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
% \caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
% \label{fig_beta_hellinger}
% \end{center}
% \end{figure*}

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
%   \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
%     \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
% \label{fig_dirichlet_hellinger}
% \end{center}
% \end{figure*}

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
%   \subfigure[accuracy measurement based on $l_1$ norm]{
%     \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
% \caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
% \label{fig_dirichlet_hellinger_l1}
% \end{center}
% \end{figure*}

% In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kinds of sensitivity and the Laplace mechanism.
% % \begin{figure*}
% % \begin{center}
% % \centering
% %   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
% %     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
% %   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
% %     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% % \caption{The experimental results of accuracy of four algorithms}
% % \label{fig_data}
% % \end{center}
% % \end{figure*}

% We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy of each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $z$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(z, \bysinfer(x))$.

% When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig. \ref{fig_beta_hellinger}. It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.

% To have more experimental results, we then extended the $\betad$ to the Dirichlet distribution $\dirichlet$ as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.

% Then, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig. \ref{fig_dirichlet_hellinger_l1}.

% The results based on $l_1$ norm are actually very similar to results based on Hellinegr distance.

% In both of the two cases, the performances of our exponential mechanism with smooth sensitivity and Laplace mechanism are very close. We can obtain some preliminary conclusions: 
% \begin{enumerate}
% 	\item Our exponential mechanism with smooth sensitivity can have similar accuracy as it with local sensitivity. Both of the two exponential mechanisms are do much better than it with global sensitivity.
% 	\item The accuracy of our exponential mechanism is better than Laplace mechanism. But the advantages are not significant.
% \end{enumerate}

% In consequence, we have a further experiments exploration on the accuracy trade-off between Laplace mechanism and our exponential mechanism in next section.

% \subsubsection{Experiment Analysis}
% In this part, we will do some experiment analysis to study the accuracy trade-off between our exponential mechanism and Laplace mechanism. By computing the two mechanisms' discrete probabilities wrt. steps (i.e., Hellinegr distance) from correct answer under different settings, we got groups of results as in Fig. \ref{fig_theory_50_50}, \ref{fig_theory_20_20_20}, \ref{fig_theory_20_20_20_20} and \ref{fig_theory_1_1_1_77}.

% Subfigs (a) based on Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. The x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. The x-axis is the Hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, we just use the Hellinger distance to label the x-axis here. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_50_50.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{50_50.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1)$, observed data $x = (49, 49) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_50_50}
% \end{center}
% \end{figure*}

% When the data size and the dimension of the prior distribution is small, our exponential mechanism can do better than Laplace, both in experiments and in theory, as shown in Fig. \ref{fig_theory_50_50}. In Subfig. \ref{fig_theory_50_50}(a), the experiment results show that the average Hellinger distance of our mechanism's outputs are smaller than Laplace mechanism, i.e., the average accuracy of our mechanism is higher than Laplace mechanism. In the mean time, the theory calculation results in Subfig. \ref{fig_theory_50_50}(b) also show that our exponential mechanism can output good answers with higher probabilities and output bad answers with lower probabilities than Laplace mechanism.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1)$, observed data $x = (20,20,20)$, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_20_20_20}, we plotted the results under the case ($x = (20,20,20)$). SubFig. \ref{fig_theory_20_20_20}(a) shows that the average accuracy of Laplace mechanism is slightly better than our mechanism. Meanwhile, the SubFig. \ref{fig_theory_20_20_20}(b) shows the Laplace mechanism have higher probabilities on some good answers but lower on some other good answers. The advantage is not significant. So, we increase the data size and the dimension in next case to have a further study.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_20_20_20_20.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{20_20_20_20.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (20,20,20,20) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_20_20_20_20}
% \end{center}
% \end{figure*}

% Here we studied the case when data size $n = 80$ and observed data set $x=(20,20,20,20)$ and plotted these discrete probabilities, shown in Fig. \ref{fig_theory_20_20_20_20}.  Subfig. \ref{fig_theory_20_20_20_20}(a) shows that the Laplace mechanism is better than our exponential mechanism very obviously. Subfig \ref{fig_theory_20_20_20_20}(b) shows that the Laplace can output most of the good answers with higher probabilities than our exponential mechanism. The advantage in the SubFig. \ref{fig_theory_20_20_20_20}(a) is obvious but still not significant in SubFig. \ref{fig_theory_20_20_20_20}(b). So, we change the variance of the observed data set in the next case.

% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[accuracy measurement based on Hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{theory_compare_1_1_1_77.eps}}
%   \subfigure[discrete probabilities wrt. hellinger distance]{
%     \includegraphics[width=0.48\textwidth]{1_1_1_77.eps}} 
% \caption{Settings: Dirichlet prior distribution $\dirichlet(1,1,1,1)$, observed data $x = (1,1,1,77) $, $\epsilon = 0.8$ and $\delta = 0.000005$}
% \label{fig_theory_1_1_1_77}
% \end{center}
% \end{figure*}

% In Fig. \ref{fig_theory_1_1_1_77}, we considered an edge case where the variance of the observed data set is small: $x=(1,1,1,77)$ and plotted these discrete probabilities. This plot can show clearly that the Laplace mechanism is much better than our exponential mechanism, both in (a) and (b). In Subfig. \ref{fig_theory_1_1_1_77}(b), the average accuracy of Laplace mechanism is conspicuously better than the other three exponential mechanisms. Also, in Subfig. \ref{fig_theory_1_1_1_77}(b), the Laplace mechanism can output good answers with much higher probabilities, even though their performances on bad answers are not so obviously. Moreover, no matter good answers or bad answers, their outputting probabilities are very close in our exponential mechanism.

% From the theory and experimental analysis above, we obtained some conclusions
% \begin{enumerate}
% 	\item when the data size and the dimensions of the prior distribution are small (candidate set size $n^{m-1}$ around 5000, our exponential mechanism with smooth sensitivity can do better than Laplace mechanism.

% 	\item when the observed data set is close to center (i.e., the variance is large), the performance of the two mechanisms are close to each other.

% 	\item The Laplace mechanism will beat us when the data size and the dimensions of the prior distribution increasing and when the variance of the observed data set is small.
% \end{enumerate}

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}

In this section, we evaluate the accuracy wrt. four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables. We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable. In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables. The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.

\subsubsection{Accuracy Evaluation wrt. Datasize}
\label{subsubsec_vs_datasize}

@@

% \subsubsection{Accuracy Evaluation wrt. Data variance}
% \label{subsubsec_vs_variance}

% In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
% of balance of the datasets. We  study this variable only under
% two-dimensions $\betad$ distribution in order to be more concise. The plot shows
% that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
% \caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
% \label{fig_vs_variance}
% \end{figure}

\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
We also considered balanced priors with increasing values in their dimensions.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
% \label{subsubsec_vs_prior_variance}

% \begin{figure}[ht]
% \centering
% \includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean.eps}
% \caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
% \label{fig_vs_prior_variance}
% \end{figure}

% Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

>>>>

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}
\usepackage{accents}

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}

\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \citet{dimitrakakis2014robust}, and
\citet{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

When the output of a differentially private mechanism is a probability
distribution, accuracy is naturally measured by means of
\emph{probabilistic distances} measuring how far this distribution is
from the original one. Some classical examples are total variation distance,
Hellinger distance, $\chi^2$-distance, KL-divergence, etc.

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with an approach based on
the Laplace mechanism.
\end{abstract}

% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
% \begin{CCSXML}
% <ccs2012>
% <concept>
% <concept_id>10002978.10003029.10011703</concept_id>
% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
% <concept_significance>500</concept_significance>
% </concept>
% </ccs2012>
% \end{CCSXML}

% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% % -- end of section to replace with generated code

\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords

\maketitle

\section{An informal motivation}
\label{sec_intro}
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to  introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.

\section{Bayesian Inference Background}
\label{sec_background}
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
\[
  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression $\Pr(\dataobs | \theta)$ denotes the
\emph{likelihood} of observing $\dataobs$ under a value of
$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distributions. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior
simplifies calculations and allows for inference to be performed in a
recursive fashion over the data.
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
Specifically, we will consider the situation where $\theta$ represents
the parameter --informally called \emph{bias}-- of a Bernoulli
distributed random variable, and its immediate generalization where
the parameter $\vtheta$ represents the vector of parameters of a
categorically distributed random variable.  In the former case, the
prior distribution over $\theta\in [0,1]$ is going to be a beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:

\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the componentwise sum of vectors of reals.

\section{The Problem Statement}
\label{sec:base}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
calculations in the case of the probabilistic models considered here
and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.

@@

\subsection{Baseline Approach - Laplace Mechanism}
\label{subsec_lap}

@@

\textbf{Detail proof:}

	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
\begin{itemize}
	\item $\lambda < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

@@

\subsection{Accuracy Analysis Comparing with Laplace mechanism}
\label{subsec_accuracy_tradeoff}
Based on accuracy study above, we are going to have a further study on the accuracy relationship between Laplace mechanism and our exponential mechanism in four aspects: data size, dimensions, prior distribution and data variance.

@@

\end{itemize}
\subsubsection{Accuracy Analysis wrt. prior distribution}

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{sensitivity}
\caption{Hellinger distance study}
\label{fig_sensitivity}
\end{figure}
In this part, we firstly study the local sensitivity of Hellinger distance of different $\betad$ distributions as in Fig. \ref{fig_sensitivity}, in order to have a better understanding of the relationships between accuracy and next two aspects.

@@

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}
In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 0.8$, and $\delta = 10^{-8}$.

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents our newly
designed exponential mechanism's behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the yellow box next to
it represents the performance of a variation of the basic Laplace
mechanism presented in Section (\ref{sec:base}) with the same
settings: that is $\epsilon, \delta$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

@@

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
We also considered balanced priors with increasing values in their dimensions.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}
